### 2013-11-15 abstract.tex
The abstract template

%%%%%  LaTeX template for submission of abstracts to  MaxEnt 2013         
%%%%%                                                         
%%%%% Use this template to generate a pdf version of your abstract for submission. This is 
%%%%% most easily accomplished using a LaTeX compiler that outputs directly to pdf.
%%%%%                                      
%%%%% Your abstract may be no more that one page in length and that all text and figures must                                                      
%%%%% fit in a 16.0 cm x 23.0 cm frame. 
%%%%%                                          
%%%%% When you submit the pdf version of your abstract on the conference web site
%%%%% you will be ask if your are requesting an Oral presentation or a Poster.  You will                             
%%%%% also be ask it this is a student presentation.                                          
%%%%%

%%%%% Do not change the text size in the line below.
\documentclass[letterpaper,12pt]{article}
%\documentclass[final,onecolumn]{aipproc}
%\layoutstyle{6x9}

%%%%%  If you chose not to include the optional figure then you can delete the line below.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

%\usepackage{empheq}   %boxes around equations
%\usepackage{multicol}        % used for the two-column index
%\usepackage[bottom]{footmisc}	% places footnotes at page bottom
%\usepackage{epstopdf} 	%essential with TeXShop on Mac
%\usepackage{longtable} 	%long tables
%\usepackage{esint}  	%multiple integral fonts
%\usepackage{stmaryrd} 	%floor, ceiling symbol font

%\hyphenation{MaxEnt}

%%%%% Page size and layout commands. Do not change lines below below.
\textwidth16cm
\textheight23cm
\topmargin-2.0cm
\oddsidemargin0cm
\parindent0pt
%\pagestyle{empty}
%%%%% End of Page size and layout commands.

\begin{document}

%%%%%  The title of your contribution in all capital letters.
\title{TITLE OF YOUR CONTRIBUTION}

%%%%%  Author's name (underline presenter's author)            
\author{\underline{F. Author}$^{1,2}$, S. Author$^{3}$\\
        (1) First Institution\\
        (2) Second Institution\\
        (3) Third Institution\\
        (You might put here additional information: e-mail,
         URL, etc)
       }

\date{date}
\maketitle

%%%%%               Abstract begins here                      
\begin{abstract}
\noindent
In this work we show how to calculate the answer to the Ultimate Question of Life, the Universe and Everything using a combination of Bayes rule and MaxEnt:
\begin{gather}
P(H|D,I) = \frac{P(D|H,I) \, P(H|I)}{P(D|I)}
\\
\mathcal{H} = - \sum_i p_i \ln \frac{p_i}{q_i}
\end{gather}
and a very large organic computer.

%%%%%       OPTIONAL: Figure (delete if not used)                                                 
%%%%%       Do not add a figure caption.
%%%%%       The conference program will not be printed in colour so colour figures should not be used.
%%%%%       The example figure is in pdf format.

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=70mm]{roo}
%\end{center}
%%\caption{blah blah.}
%%\label{fig:roo}
%\end{figure}
%%%%%        End of Figure

%%%%%       OPTIONAL: References (delete  if not used)   
%%%%%       Separate each reference with a blank line.                                                                
\medskip\noindent{References: }

[1] A. Dent et al. Phys. Rev. {\bf E99}, 99998 (2009).

[2] Z. Beeblebrox et al. Phys. Rev. {\bf E99}, 99999 (2009).
%%%%%        END of References

%%%%%       OPTIONAL: Key Words (delete if not used)   
\medskip\noindent{Key Words: }
{Jaynes, Deep Thought, Marsupials}
%%%%%        END of Key Words

\end{abstract}
\thispagestyle{empty}
\end{document}

\endinput

### 2013-11-15 abstract.tex
Brain dump

@@
 %%%%%  The title of your contribution in all capital letters.
-\title{TITLE OF YOUR CONTRIBUTION}
+\title{ASTRONOMICAL INFERENCE WITH DIFFUSIVE NESTED SAMPLING}
 
 %%%%%  Author's name (underline presenter's author)            
-\author{\underline{F. Author}$^{1,2}$, S. Author$^{3}$\\
-        (1) First Institution\\
-        (2) Second Institution\\
-        (3) Third Institution\\
-        (You might put here additional information: e-mail,
-         URL, etc)
+\author{\underline{Brendon J. Brewer}$^{1}$\\
+        (1) Department of Statistics, The University of Auckland\\
+	\\
+        {\tt http://stat.auckland.ac.nz/\~{ }brewer/}
        }
 
-\date{date}
+\date{}
 \maketitle
@@
 \noindent
-In this work we show how to calculate the answer to the Ultimate Question of Life, the Universe and Everything using a combination of Bayes rule and MaxEnt:
-\begin{gather}
-P(H|D,I) = \frac{P(D|H,I) \, P(H|I)}{P(D|I)}
-\\
-\mathcal{H} = - \sum_i p_i \ln \frac{p_i}{q_i}
-\end{gather}
-and a very large organic computer.
+
+Many standard problems in astronomy (e.g. the processing of images to produce
+``catalogs'') are best understood as inference problems. In principle at least,
+we should calculate the posterior distribution over a suitable hypothesis space,
+rather than inventing ad-hoc procedures.
+
+I will describe the Diffusive Nested Sampling method, which is a variant of
+Nested Sampling that retains the flexibility of Markov Chain Monte Carlo
+exploration of the hypothesis space.
+
+Talk about the StarField project
+Talk about Reverberation Mapping
+Talk about how Nested Sampling is hard when you need to compress so far
+Talk about reversible jump
 
@@
 \medskip\noindent{Key Words: }
-{Jaynes, Deep Thought, Marsupials}
+{Bayesian Inference, Markov Chain Monte Carlo}
 %%%%%        END of Key Words

### 2013-11-18 abstract.tex
Abstract done

@@
 %%%%%  The title of your contribution in all capital letters.
-\title{ASTRONOMICAL INFERENCE WITH DIFFUSIVE NESTED SAMPLING}
+\title{COMPUTING ASTROPHYSICAL INFERENCES WITH DIFFUSIVE NESTED SAMPLING}
 
@@
 
-Many standard problems in astronomy (e.g. the processing of images to produce
-``catalogs'') are best understood as inference problems. In principle at least,
+Many standard problems in astronomy are best understood as inference problems.
+In principle at least,
 we should calculate the posterior distribution over a suitable hypothesis space,
-rather than inventing ad-hoc procedures.
+rather than inventing ad-hoc procedures. I will describe two recent applications
+of this idea: i) inferring the properties of active galactic nuclei (AGN)
+from reverberation mapping data, and ii) producing ``catalogs'' from images of
+crowded stellar fields. The first application allows us to measure the masses
+of black holes and to infer the dynamical state of the matter surrounding them,
+making the most of the large amount of telescope time required. The second
+application has the potential to enable the study of faint objects that are not
+even ``detected'' by standard algorithms.
+To implement these models we used the ``Diffusive Nested Sampling'' algorithm,
+which is a variant of Nested Sampling that was invented at MaxEnt 2009. The
+algorithm naturally allows for unknown numbers of parameters since
+``reversible jump MCMC'' can be used inside of it. However, there are
+computational challenges involved when the posterior distribution is highly
+compressed with respect to the prior distribution.
 
-I will describe the Diffusive Nested Sampling method, which is a variant of
-Nested Sampling that retains the flexibility of Markov Chain Monte Carlo
-exploration of the hypothesis space.
-
-Talk about the StarField project
-Talk about Reverberation Mapping
-Talk about how Nested Sampling is hard when you need to compress so far
-Talk about reversible jump
-
-%%%%%       OPTIONAL: Figure (delete if not used)                                                 
-%%%%%       Do not add a figure caption.
-%%%%%       The conference program will not be printed in colour so colour figures should not be used.
-%%%%%       The example figure is in pdf format.
-
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=70mm]{roo}
-%\end{center}
-%%\caption{blah blah.}
-%%\label{fig:roo}
-%\end{figure}
-%%%%%        End of Figure
-
-%%%%%       OPTIONAL: References (delete  if not used)   
-%%%%%       Separate each reference with a blank line.                                                                
+\vspace{1cm}
 \medskip\noindent{References: }
 
-[1] A. Dent et al. Phys. Rev. {\bf E99}, 99998 (2009).
+[1] {\it Diffusive Nested Sampling}\\
+Brendon J. Brewer, Livia B. P{\'a}rtay, Gabor Cs{\'a}nyi,
+Statistics and Computing, 2011, 21, 4, 649-656.\\
 
-[2] Z. Beeblebrox et al. Phys. Rev. {\bf E99}, 99999 (2009).
+[2] {\it Geometric and Dynamical Models of Reverberation Mapping Data}\\
+Anna Pancoast, Brendon J. Brewer, Tommaso Treu, 2011, ApJ, 730, 139.\\
+
+[3] {\it Probabilistic Catalogs for Crowded Stellar Fields}\\
+Brendon J. Brewer, Daniel Foreman-Mackey, David W. Hogg, 2013, AJ, 146, 7.\\
 %%%%%        END of References
@@
 \medskip\noindent{Key Words: }
-{Bayesian Inference, Markov Chain Monte Carlo}
+{Astrophysics, Bayesian Inference, Markov Chain Monte Carlo}
 %%%%%        END of Key Words

### 2013-11-18 abstract.tex
Reduced number of scare quotes

@@
 of this idea: i) inferring the properties of active galactic nuclei (AGN)
-from reverberation mapping data, and ii) producing ``catalogs'' from images of
+from reverberation mapping data, and ii) producing catalogs (lists of objects
+and their properties) from images of
 crowded stellar fields. The first application allows us to measure the masses
@@
 even ``detected'' by standard algorithms.
-To implement these models we used the ``Diffusive Nested Sampling'' algorithm,
+To implement these models we used the Diffusive Nested Sampling algorithm,
 which is a variant of Nested Sampling that was invented at MaxEnt 2009. The
 algorithm naturally allows for unknown numbers of parameters since
-``reversible jump MCMC'' can be used inside of it. However, there are
+``reversible jump'' MCMC can be used inside of it. However, there are
 computational challenges involved when the posterior distribution is highly

### 2013-11-26 ms.tex
Beginning the manuscript

--- 2013-11-18 abstract.tex
@@
-%%%%%  LaTeX template for submission of abstracts to  MaxEnt 2013         
-%%%%%                                                         
-%%%%% Use this template to generate a pdf version of your abstract for submission. This is 
-%%%%% most easily accomplished using a LaTeX compiler that outputs directly to pdf.
-%%%%%                                      
-%%%%% Your abstract may be no more that one page in length and that all text and figures must                                                      
-%%%%% fit in a 16.0 cm x 23.0 cm frame. 
-%%%%%                                          
-%%%%% When you submit the pdf version of your abstract on the conference web site
-%%%%% you will be ask if your are requesting an Oral presentation or a Poster.  You will                             
-%%%%% also be ask it this is a student presentation.                                          
-%%%%%
+\documentclass[letterpaper, 11pt]{article}
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage[left=3cm,top=3cm,right=3cm]{geometry}
 
-%%%%% Do not change the text size in the line below.
-\documentclass[letterpaper,12pt]{article}
-%\documentclass[final,onecolumn]{aipproc}
-%\layoutstyle{6x9}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\textfraction}{0.1}
+\parindent=0cm
 
-%%%%%  If you chose not to include the optional figure then you can delete the line below.
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-%\usepackage{empheq}   %boxes around equations
-%\usepackage{multicol}        % used for the two-column index
-%\usepackage[bottom]{footmisc}	% places footnotes at page bottom
-%\usepackage{epstopdf} 	%essential with TeXShop on Mac
-%\usepackage{longtable} 	%long tables
-%\usepackage{esint}  	%multiple integral fonts
-%\usepackage{stmaryrd} 	%floor, ceiling symbol font
-
-%\hyphenation{MaxEnt}
-
-%%%%% Page size and layout commands. Do not change lines below below.
-\textwidth16cm
-\textheight23cm
-\topmargin-2.0cm
-\oddsidemargin0cm
-\parindent0pt
-%\pagestyle{empty}
-%%%%% End of Page size and layout commands.
+\title{Document Title}
+\author{Brendon J. Brewer}
 
 \begin{document}
-
-%%%%%  The title of your contribution in all capital letters.
-\title{COMPUTING ASTROPHYSICAL INFERENCES WITH DIFFUSIVE NESTED SAMPLING}
-
-%%%%%  Author's name (underline presenter's author)            
-\author{\underline{Brendon J. Brewer}$^{1}$\\
-        (1) Department of Statistics, The University of Auckland\\
-	\\
-        {\tt http://stat.auckland.ac.nz/\~{ }brewer/}
-       }
-
-\date{}
 \maketitle
 
-%%%%%               Abstract begins here                      
-\begin{abstract}
-\noindent
-
-Many standard problems in astronomy are best understood as inference problems.
+\abstract{Many standard problems in astronomy are best understood as inference problems.
 In principle at least,
@@
 computational challenges involved when the posterior distribution is highly
-compressed with respect to the prior distribution.
+compressed with respect to the prior distribution.}
 
-\vspace{1cm}
-\medskip\noindent{References: }
-
-[1] {\it Diffusive Nested Sampling}\\
-Brendon J. Brewer, Livia B. P{\'a}rtay, Gabor Cs{\'a}nyi,
-Statistics and Computing, 2011, 21, 4, 649-656.\\
-
-[2] {\it Geometric and Dynamical Models of Reverberation Mapping Data}\\
-Anna Pancoast, Brendon J. Brewer, Tommaso Treu, 2011, ApJ, 730, 139.\\
-
-[3] {\it Probabilistic Catalogs for Crowded Stellar Fields}\\
-Brendon J. Brewer, Daniel Foreman-Mackey, David W. Hogg, 2013, AJ, 146, 7.\\
-%%%%%        END of References
-
-%%%%%       OPTIONAL: Key Words (delete if not used)   
-\medskip\noindent{Key Words: }
-{Astrophysics, Bayesian Inference, Markov Chain Monte Carlo}
-%%%%%        END of Key Words
-
-\end{abstract}
-\thispagestyle{empty}
 \end{document}
-
-\endinput

### 2013-12-08 ms.tex
AIS template

@@
-\documentclass[letterpaper, 11pt]{article}
-\usepackage{graphicx}
-\usepackage{natbib}
-\usepackage[left=3cm,top=3cm,right=3cm]{geometry}
+%%
+%% This is file `template-8s.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% template.raw  (with options: `8s')
+%% 
+%% Template for the LaTeX class aipproc.
+%% 
+%% (C) 1998,2000,2001 American Institute of Physics and Frank Mittelbach
+%% All rights reserved
+%% 
+%%
+%% $Id: template.raw,v 1.12 2005/07/06 19:22:14 frank Exp $
+%%
 
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\textfraction}{0.1}
-\parindent=0cm
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please remove the next line of code if you
+%% are satisfied that your installation is
+%% complete and working.
+%%
+%% It is only there to help you in detecting
+%% potential problems.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\title{Document Title}
-\author{Brendon J. Brewer}
+\input{aipcheck}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% SELECT THE LAYOUT
+%%
+%% The class supports further options.
+%% See aipguide.pdf for details.
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[
+    ,final            % use final for the camera ready runs
+%%  ,draft            % use draft while you are working on the paper
+%%  ,numberedheadings % uncomment this option for numbered sections
+%%  ,                 % add further options here if necessary
+  ]
+  {aipproc}
+
+\layoutstyle{8x11single}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% FRONTMATTER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
+
+\title{Computing astrophysical inferences with diffusive nested sampling}
+
+\classification{<Replace this text with PACS numbers; choose from this list:
+                \texttt{http://www.aip..org/pacs/index.html}>}
+\keywords      {<Enter Keywords here>}
+
+\author{Brendon J. Brewer}{
+  address={http://stat.auckland.ac.nz/~brewer/}
+}
+
+\author{<author2>}{
+  address={<common address for author2 and author3>}
+}
+
+\author{<author3>}{
+  address={<common address for author2 and author3>}
+  ,altaddress={<author1 address>} % additional visiting address
+}
+
+\begin{abstract}
+The abstract.
+\end{abstract}
+
 \maketitle
 
-\abstract{Many standard problems in astronomy are best understood as inference problems.
-In principle at least,
-we should calculate the posterior distribution over a suitable hypothesis space,
-rather than inventing ad-hoc procedures. I will describe two recent applications
-of this idea: i) inferring the properties of active galactic nuclei (AGN)
-from reverberation mapping data, and ii) producing catalogs (lists of objects
-and their properties) from images of
-crowded stellar fields. The first application allows us to measure the masses
-of black holes and to infer the dynamical state of the matter surrounding them,
-making the most of the large amount of telescope time required. The second
-application has the potential to enable the study of faint objects that are not
-even ``detected'' by standard algorithms.
-To implement these models we used the Diffusive Nested Sampling algorithm,
-which is a variant of Nested Sampling that was invented at MaxEnt 2009. The
-algorithm naturally allows for unknown numbers of parameters since
-``reversible jump'' MCMC can be used inside of it. However, there are
-computational challenges involved when the posterior distribution is highly
-compressed with respect to the prior distribution.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% MAINMATTER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% BACKMATTER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{theacknowledgments}
+Acknowledgements.
+\end{theacknowledgments}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The bibliography can be prepared using the BibTeX program or
+%% manually.
+%%
+%% The code below assumes that BibTeX is used.  If the bibliography is
+%% produced without BibTeX comment out the following lines and see the
+%% aipguide.pdf for further information.
+%%
+%% For your convenience a manually coded example is appended
+%% after the \end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% You may have to change the BibTeX style below, depending on your
+%% setup or preferences.
+%%
+%%
+%% For The AIP proceedings layouts use either
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{aipproc}   % if natbib is available
+%\bibliographystyle{aipprocl} % if natbib is missing
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% You probably want to use your own bibtex database here
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\bibliography{sample}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Just a reminder that you may have to run bibtex
+%%% All of it up to \end{document} can be removed
+%%% if you don't like the warning.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\IfFileExists{\jobname.bbl}{}
+% {\typeout{}
+%  \typeout{******************************************}
+%  \typeout{** Please run "bibtex \jobname" to optain}
+%  \typeout{** the bibliography and then re-run LaTeX}
+%  \typeout{** twice to fix the references!}
+%  \typeout{******************************************}
+%  \typeout{}
+% }
 
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The following lines show an example how to produce a bibliography
+%% without the help of the BibTeX program. This could be used instead
+%% of the above.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{thebibliography}{9}
+
+\bibitem{Brown2000}
+M.~P. Brown,  and K.~Austin, \emph{The New Physique}, Publisher Name,
+  Publisher City, 2000, pp. 212--213.
+
+\bibitem{BrownAustin:2000}
+M.~P. Brown,  and K.~Austin, \emph{Appl. Phys. Letters} \textbf{85},
+  2503--2504 (2000).
+
+\bibitem{Wang}
+R.~Wang, ``Title of Chapter,'' in \emph{Classic Physiques}, edited by
+  R.~B. Hamil, Publisher Name, Publisher City, 2000, pp. 212--213.
+
+\bibitem{SJ:1999}
+C.~D.~Smith and E.~F.~Jones,  ``Load-Cycling in Cubic Press,'' in
+  \emph{Shock Compression of Condensed Matter-1999}, edited by M.~D.~F. et~al.,
+  AIP Conference Proceedings 505, American Institute of Physics, New York,
+  1999, pp. 651--654.
+
+\end{thebibliography}
+
+\endinput
+%%
+%% End of file `template-8s.tex'.

### 2013-12-08 ms.tex
Abstract

@@
                 \texttt{http://www.aip..org/pacs/index.html}>}
-\keywords      {<Enter Keywords here>}
+\keywords      {Astrophysics -- Bayesian Inference -- Nested Sampling}
 
 \author{Brendon J. Brewer}{
-  address={http://stat.auckland.ac.nz/~brewer/}
-}
-
-\author{<author2>}{
-  address={<common address for author2 and author3>}
-}
-
-\author{<author3>}{
-  address={<common address for author2 and author3>}
-  ,altaddress={<author1 address>} % additional visiting address
+  address={Department of Statistics, The University of Auckland\\
+http://stat.auckland.ac.nz/\~{ }brewer/}
 }
@@
 \begin{abstract}
-The abstract.
+Many standard problems in astronomy are best understood as inference problems.
+In principle at least,
+we should calculate the posterior distribution over a suitable hypothesis space,
+rather than inventing ad-hoc procedures. I will describe two recent applications
+of this idea: i) inferring the properties of active galactic nuclei (AGN)
+from reverberation mapping data, and ii) producing catalogs (lists of objects
+and their properties) from images of
+crowded stellar fields. The first application allows us to measure the masses
+of black holes and to infer the dynamical state of the matter surrounding them,
+making the most of the large amount of telescope time required. The second
+application has the potential to enable the study of faint objects that are not
+even ``detected'' by standard algorithms.
+To implement these models we used the Diffusive Nested Sampling algorithm,
+which is a variant of Nested Sampling that was invented at MaxEnt 2009. The
+algorithm naturally allows for unknown numbers of parameters since
+``reversible jump'' MCMC can be used inside of it. However, there are
+computational challenges involved when the posterior distribution is highly
+compressed with respect to the prior distribution.
 \end{abstract}

### 2013-12-08 ms.tex
Product rule
Writing

@@
 \layoutstyle{8x11single}
+\usepackage{amsmath}
+\usepackage{dsfont}
+
+\newcommand{\pars}{\boldsymbol{\theta}}
+\newcommand{\data}{\mathbf{x}}
 
@@
 \section{Introduction}
+
+A joint prior is assigned on the hypothesis space of possible $\pars$ values
+and possible data sets $\data$:
+\begin{eqnarray}
+p(\pars, \data) = p(\pars) p(\data | \pars) = p(\data)p(\pars | \data)
+\end{eqnarray}
+The marginal distribution $p(\pars)$, which is usually called the ``prior'',
+describes initial uncertainty about the value of the parameters. When the
+data $\data$ becomes known, our state of knowledge about $\pars$ changes
+from the marginal $p(\pars)$ to the conditional distribution $p(\pars | \data)$
+that corresponds to the observed data, usually called the ``posterior''.
+Incidentally, Bayesian inference can be understood as a special case of
+MaxEnt updating, starting from the joint prior $p(\pars, \data)$ and applying
+the constraint $P(\data = \data_{\rm actual}) = 1$ \citep{caticha}. Note that
+this is not a ``derivation'' of Bayesian updating as the rules of probability
+already imply a commitment to update to $p(\pars | \data)$ once $\data$ becomes
+known (what else could a conditional probability be?).
+
+\section{Probabilistic Catalogs}
+The hypothesis space is the set of possible answers to the question
+``how many objects are there, and what are their properties (positions, fluxes,
+etc)''.
+
+\section{Reverberation Mapping}
+Many objects in the universe are too distant to resolve, so we cannot simply
+``see'' what is going on. Rather we must infer what is going on. Active Galactic
+Nuclei (AGN) are a good example.
+
+\subsection{Models with known oversimplifications}
+Computing the posterior $p(\pars | \data)$ would yield overconfident results
+since the assumed model is known to be wrong. However certain parameters still
+``exist'' (such as the black hole mass) and we want our posterior inferences
+to be realistic.
+
+We have been using the following subjective procedure. Later we give two
+interpretations of this procedure which may lead the way to less subjective
+approaches.
+Using DNS we explore the mixture of constrained priors.
+\begin{eqnarray}
+p_{\rm DNS}(\theta) &=& \sum_{i=1}^n p(\theta)\mathds{1}\left[\mathcal{L} > L^*_i\right]
+\end{eqnarray}
 

### 2014-01-05 ms.tex
Random words
Intro sentence

@@
 \section{Introduction}
+The major goal of astronomy, as with most sciences, is to understand the
+universe as well as we can while recognising that we will never have all of
+the relevant information that we might want.
 
@@
 known (what else could a conditional probability be?).
+
+\section{Diffusive Nested Sampling}
+DNS is essentially just the Metropolis algorithm. However, instead of the
+target distribution being the posterior $p(\pars|\data)$, it is the mixture
+of constrained priors.
 
@@
 \begin{eqnarray}
-p_{\rm DNS}(\theta) &=& \sum_{i=1}^n p(\theta)\mathds{1}\left[\mathcal{L} > L^*_i\right]
+p_{\rm DNS}(\theta) &=& \frac{1}{n}\sum_{i=1}^n
+\frac{p(\theta)\mathds{1}\left[L(\theta) > L^*_i\right]}{X_i}
 \end{eqnarray}
+where $X_i \approx e^{-i}$ by construction.
 

### 2014-01-06 ms.tex
Sentences
Slight edits

@@
 
-A joint prior is assigned on the hypothesis space of possible $\pars$ values
-and possible data sets $\data$:
+In many subfields within astronomy, Bayesian inference has (rightfully)
+become the dominant framework for analysing data and quantifying the
+plausibility of hypotheses about the universe.
+
+The first step is to construct a set of possible answers to the question of
+interest, that is, the ``hypothesis space'', indexed by parameters $\pars$.
+A space of possible data sets $\data$ is considered, and a joint prior is
+assigned:
 \begin{eqnarray}

### 2014-01-14 ms.tex
Slight amount of writing

@@
 become the dominant framework for analysing data and quantifying the
-plausibility of hypotheses about the universe.
+plausibility of hypotheses about the universe \citep[e.g.][]{refs}.
 
@@
 DNS is essentially just the Metropolis algorithm. However, instead of the
-target distribution being the posterior $p(\pars|\data)$, it is the mixture
-of constrained priors.
+target distribution being the posterior $p(\pars|\data)$, the algorithm
+constructs and then samples a ``mixture of constrained priors'':
+
+\begin{eqnarray}
+p_{\rm DNS}(\theta) &=& \frac{1}{n}\sum_{i=1}^n
+\frac{p(\theta)\mathds{1}\left[L(\theta) > L^*_i\right]}{X_i}
+\end{eqnarray}
+
+The zeroth component of this mixture is just the prior $p(\pars)$. The first
+mixture component is the prior, but restricted to the domain where the
+likelihood is greater than a threshold $L^*_1$. The second mixture component
+is the prior, but restricted to the domain where the likelihood is above
+$L^*_2$. The likelihood thresholds $\{ L^*_i \}$ are chosen so each
+successive constrained prior occupies approximately $\exp(-1)$ times as much
+prior mass (``volume'') as the previous constrained prior.
 
@@
 Using DNS we explore the mixture of constrained priors.
-\begin{eqnarray}
-p_{\rm DNS}(\theta) &=& \frac{1}{n}\sum_{i=1}^n
-\frac{p(\theta)\mathds{1}\left[L(\theta) > L^*_i\right]}{X_i}
-\end{eqnarray}
+
 where $X_i \approx e^{-i}$ by construction.

### 2014-01-28 ms.tex
Intro work

@@
 universe as well as we can while recognising that we will never have all of
-the relevant information that we might want.
+the relevant information that we might want. Probability theory is the
+appropriate framework for describing and quantifying uncertainty
+\citep{cox, jaynes}. In recent years, Bayesian inference has (rightfully)
+become the dominant framework for analysing data and quantifying the
+plausibility of hypotheses about the universe, and has displaced
+more ad-hoc methodologies in many subfields of
+astronomy \citep[e.g.][]{examples}.
 
-In many subfields within astronomy, Bayesian inference has (rightfully)
-become the dominant framework for analysing data and quantifying the
-plausibility of hypotheses about the universe \citep[e.g.][]{refs}.
+Bayesian inference is usually performed by
+constructing a set of possible answers to the question of
+interest, that is, the ``hypothesis space'', indexed by parameters $\pars$.
+A state of prior knowledge about the parameters is described by assigning a
+prior distribution $p(\pars)$. Some relevant data $\data$ is about to become
+known, and prior knowledge about a connection between $\theta$ and $\data$ is
+expressed by a choice of ``sampling distribution'' $p(\data | \theta)$, which
+is really a family of probability distributions, one for each possible value of
+$\theta$.
 
-The first step is to construct a set of possible answers to the question of
-interest, that is, the ``hypothesis space'', indexed by parameters $\pars$.
-A space of possible data sets $\data$ is considered, and a joint prior is
-assigned:
+By the product rule, the joint (prior) distribution is
 \begin{eqnarray}
@@
 \end{eqnarray}
-The marginal distribution $p(\pars)$, which is usually called the ``prior'',
-describes initial uncertainty about the value of the parameters. When the
+When the
 data $\data$ becomes known, our state of knowledge about $\pars$ changes
-from the marginal $p(\pars)$ to the conditional distribution $p(\pars | \data)$
-that corresponds to the observed data, usually called the ``posterior''.
+from the marginal $p(\pars)$ to the conditional distribution
+$p(\pars | \data_{\rm actual})$
+that corresponds to the observed data. The distribution
+$p(\pars | \data_{\rm actual})$
+called the ``posterior''.
 Incidentally, Bayesian inference can be understood as a special case of
@@
 this is not a ``derivation'' of Bayesian updating as the rules of probability
-already imply a commitment to update to $p(\pars | \data)$ once $\data$ becomes
-known (what else could a conditional probability be?).
+already imply a commitment to update from $p(\theta)$ to $p(\theta | \data)$
+once $\data$ becomes known.
+
+Computing the consequences of a posterior distribution can be a challenging
+task. Usually we want to marginalise out nuisance parameters, to compute
+particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
+the posterior distribution for easy communication with others.
+Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
+for achieving these goals.
 

### 2014-01-31 ms.tex
MCMC is hard because
Random trivial work

@@
 Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
-for achieving these goals.
+for achieving these goals. However, many standard MCMC algorithms are not
+capable of exploring complicated probability distributions in a reasonable time.
+Problems often occur due to multimodality, strong dependencies, and phase
+transitions.
 
-\section{Diffusive Nested Sampling}
-DNS is essentially just the Metropolis algorithm. However, instead of the
+\section{Nested sampling}
+The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
+should start from the prior $\pi(\pars)$ and move through a sequence of
+distributions that successively compress the prior volume by a constant factor
+that is (approximately) known.
+
+\subsection{MCMC inside nested sampling}
+
+\section{Diffusive nested sampling}
+Diffusive Nested Sampling (DNS) is an alternative to the use of MCMC inside of
+standard Nested Sampling. DNS is essentially just the Metropolis algorithm.
+However, instead of the
 target distribution being the posterior $p(\pars|\data)$, the algorithm
@@
 
-\section{Reverberation Mapping}
-Many objects in the universe are too distant to resolve, so we cannot simply
-``see'' what is going on. Rather we must infer what is going on. Active Galactic
-Nuclei (AGN) are a good example.
+%\section{Reverberation Mapping}
+%Many objects in the universe are too distant to resolve, so we cannot simply
+%``see'' what is going on. Rather we must infer what is going on. Active Galactic
+%Nuclei (AGN) are a good example.
 

### 2014-02-01 ms.tex
Wrote some words

@@
 \subsection{MCMC inside nested sampling}
+The main challenge in Nested Sampling is to generate new points from the
+constrained prior distribution $\propto \pi(\pars)\mathds{1}(L(\pars) > L^*)$.
+Two popular strategies are in use. The first is to use the remaining ``live
+points'', which are known to be above the likelihood threshold $L^*$, to build
+an approximation to the constrained prior, which can then be used to generate
+a new point via rejection sampling \citep{multinest}.
+
+The second common strategy is to use MCMC. Since the remaining live points are
+known to exceed the likelihood threshold, they can be used to initialise an
+MCMC run. This strategy is very simple but has known issues.
 

### 2014-02-03 ms.tex
The problem with copying

@@
 known to exceed the likelihood threshold, they can be used to initialise an
-MCMC run. This strategy is very simple but has known issues.
+MCMC run. This strategy is very simple but has known problems. For example,
+suppose the likelihood function has two separate modes, and it impossible for
+MCMC to mix between the two modes. Suppose also that NS is being run with two
+points, and there is one point in each mode. The worst point will be discarded
+(and its information saved elsewhere), and the new point will be generated by
+copying the other point and running MCMC. However, even though the two modes
+are completely equivalent, the copying operation will remove one of the modes,
+and it will never return.
 

### 2014-02-23 ms.tex
Simulated tempering
Fixed url

@@
   address={Department of Statistics, The University of Auckland\\
-http://stat.auckland.ac.nz/\~{ }brewer/}
+http://www.stat.auckland.ac.nz/\~{ }brewer/}
 }
@@
 successive constrained prior occupies approximately $\exp(-1)$ times as much
-prior mass (``volume'') as the previous constrained prior.
+prior mass (``volume'') as the previous constrained prior. This is strongly
+related to the algorithm known as ``simulated tempering''
+\citep{simulated_tempering}, but uses NS's
+sequence of intermediate distributions instead of an annealed sequence.
 

### 2014-02-23 ms.tex
A bunch of references

@@
 \usepackage{dsfont}
+\usepackage{natbib}
 
@@
 we should calculate the posterior distribution over a suitable hypothesis space,
-rather than inventing ad-hoc procedures. I will describe two recent applications
-of this idea: i) inferring the properties of active galactic nuclei (AGN)
-from reverberation mapping data, and ii) producing catalogs (lists of objects
+rather than inventing ad-hoc procedures. I will describe a recent application
+of this idea to the challenging astronomical problem of
+producing catalogs (lists of objects
 and their properties) from images of
-crowded stellar fields. The first application allows us to measure the masses
-of black holes and to infer the dynamical state of the matter surrounding them,
-making the most of the large amount of telescope time required. The second
-application has the potential to enable the study of faint objects that are not
+crowded stellar fields. This approach
+has the potential to enable the study of faint objects that are not
 even ``detected'' by standard algorithms.
-To implement these models we used the Diffusive Nested Sampling algorithm,
+To implement the model we used the Diffusive Nested Sampling algorithm,
 which is a variant of Nested Sampling that was invented at MaxEnt 2009. The
@@
 more ad-hoc methodologies in many subfields of
-astronomy \citep[e.g.][]{examples}.
+astronomy \citep[e.g.][]{2014MNRAS.438..768S, 2014MNRAS.437.3540F,
+2014MNRAS.437.3004L}.
 
@@
 is really a family of probability distributions, one for each possible value of
-$\theta$.
-
-By the product rule, the joint (prior) distribution is
+$\theta$. By the product rule, the joint (prior) distribution is
 \begin{eqnarray}
@@
 data $\data$ becomes known, our state of knowledge about $\pars$ changes
-from the marginal $p(\pars)$ to the conditional distribution
+from the marginal distribution $p(\pars)$ to the conditional distribution
 $p(\pars | \data_{\rm actual})$
 that corresponds to the observed data. The distribution
-$p(\pars | \data_{\rm actual})$
+$p(\pars | \data_{\rm actual})$ is
 called the ``posterior''.
@@
 ``how many objects are there, and what are their properties (positions, fluxes,
-etc)''.
+etc)'' \citep{starfield}.
 
@@
 
+\begin{thebibliography}{9}
+
+\bibitem[Brewer et al.(2013)]{starfield} Brewer, B.~J., 
+Foreman-Mackey, D., Hogg, D.~W.\ 2013.\ Probabilistic Catalogs for Crowded 
+Stellar Fields.\ The Astronomical Journal 146, 7.
+
+\bibitem[Brewer et al.(2011)]{dnest}
+Brewer, B.~J., P\'{a}rtay, L.~B., Cs\'{a}nyi, G.\ 2011.\
+Diffusive Nested Sampling.\ Statistics and Computing, 2011, 21, 4, 649-656.
+
+\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
+on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
+arXiv:0808.0012.
+
+\bibitem[Cox(1946)]{cox} Cox, R.~T.\ 1946.\ Probability, 
+Frequency and Reasonable Expectation.\ American Journal of Physics 14, 
+1-13.
+
+\bibitem[Feroz et al.(2009)]{multinest} Feroz, F., Hobson, M.~P., 
+Bridges, M.\ 2009.\ MULTINEST: an efficient and robust Bayesian inference 
+tool for cosmology and particle physics.\ Monthly Notices of the Royal 
+Astronomical Society 398, 1601-1614.
+
+\bibitem[Feroz and Hobson(2014)]{2014MNRAS.437.3540F} Feroz, F., Hobson, 
+M.~P.\ 2014.\ Bayesian analysis of radial velocity data of GJ667C with 
+correlated noise: evidence for only two planets.\ Monthly Notices of the 
+Royal Astronomical Society 437, 3540-3549.
+
+\bibitem[Jaynes and Bretthorst(2003)]{jaynes} Jaynes, E.~T., 
+Bretthorst, G.~L.\ 2003.\ Probability Theory.\ Probability Theory, by 
+E.~T.~Jaynes and Edited by G.~Larry Bretthorst, pp.~758.~ISBN 
+0521592712.~Cambridge, UK: Cambridge University Press, June 2003.\ .
+
+\bibitem[Lentati et al.(2014)]{2014MNRAS.437.3004L} Lentati, L., Alexander, 
+P., Hobson, M.~P., Feroz, F., van Haasteren, R., Lee, K.~J., Shannon, 
+R.~M.\ 2014.\ TEMPONEST: a Bayesian approach to pulsar timing analysis.\ 
+Monthly Notices of the Royal Astronomical Society 437, 3004-3023.
+
+\bibitem[Marinari and Parisi(1992)]{simulated_tempering} Marinari, E., 
+Parisi, G.\ 1992.\ Simulated tempering: a new Monte Carlo scheme.\ EPL 
+(Europhysics Letters) 19, 451.
+
+\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, J., 2006, Nested Sampling for General Bayesian Computation, Bayesian Analysis 4, pp. 833-860.
+
+\bibitem[Sutter et al.(2014)]{2014MNRAS.438..768S} Sutter, P.~M., Wandelt, 
+B.~D., McEwen, J.~D., Bunn, E.~F., Karakci, A., Korotkov, A., Timbie, P., 
+Tucker, G.~S., Zhang, L.\ 2014.\ Probabilistic image reconstruction for 
+radio interferometers.\ Monthly Notices of the Royal Astronomical Society 
+438, 768-778.
+
+\end{thebibliography}
+
 \end{document}
@@
 
-\begin{thebibliography}{9}
-
-\bibitem{Brown2000}
-M.~P. Brown,  and K.~Austin, \emph{The New Physique}, Publisher Name,
-  Publisher City, 2000, pp. 212--213.
-
-\bibitem{BrownAustin:2000}
-M.~P. Brown,  and K.~Austin, \emph{Appl. Phys. Letters} \textbf{85},
-  2503--2504 (2000).
-
-\bibitem{Wang}
-R.~Wang, ``Title of Chapter,'' in \emph{Classic Physiques}, edited by
-  R.~B. Hamil, Publisher Name, Publisher City, 2000, pp. 212--213.
-
-\bibitem{SJ:1999}
-C.~D.~Smith and E.~F.~Jones,  ``Load-Cycling in Cubic Press,'' in
-  \emph{Shock Compression of Condensed Matter-1999}, edited by M.~D.~F. et~al.,
-  AIP Conference Proceedings 505, American Institute of Physics, New York,
-  1999, pp. 651--654.
-
-\end{thebibliography}
-
 \endinput

### 2014-02-23 ms.tex
Minor edits

@@
 Problems often occur due to multimodality, strong dependencies, and phase
-transitions.
+transitions. Many different solutions have been suggested for overcoming these
+challenges. In this paper we will focus on Nested Sampling \citep{skilling}.
 
@@
 The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
-should start from the prior $\pi(\pars)$ and move through a sequence of
+should begin from the prior $\pi(\pars)$ and move through a sequence of
 distributions that successively compress the prior volume by a constant factor

### 2014-02-23 ms.tex
A figure

@@
 an approximation to the constrained prior, which can then be used to generate
-a new point via rejection sampling \citep{multinest}.
+a new point via rejection sampling, as implemented in the
+{\tt MultiNest} program \citep{multinest}.
 
-The second common strategy is to use MCMC. Since the remaining live points are
-known to exceed the likelihood threshold, they can be used to initialise an
-MCMC run. This strategy is very simple but has known problems. For example,
+The second common strategy is to use MCMC. Since all of the Nested Sampling
+points are
+known to exceed the likelihood threshold (which is defined using the lowest
+point), they can be used to initialise an
+MCMC run. This strategy is very simple to implement but can have
+serious problems. For example,
 suppose the likelihood function has two separate modes, and it impossible for
@@
 sequence of intermediate distributions instead of an annealed sequence.
+Retaining ``old'' distributions in the mixture allows
 

### 2014-03-06 ms.tex
Minor writing

@@
 Computing the consequences of a posterior distribution can be a challenging
-task. Usually we want to marginalise out nuisance parameters, to compute
+task. Usually we want to marginalise away nuisance parameters, to compute
 particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
-the posterior distribution for easy communication with others.
+the posterior distribution for easy communication with others, for example by
+calculating credible intervals and stating that $a \leq \theta b$ with 95\%
+probability.
 Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
@@
 capable of exploring complicated probability distributions in a reasonable time.
-Problems often occur due to multimodality, strong dependencies, and phase
+Problems often occur due to multiple modes, strong dependencies
+between parameters, and (less widely recognised, but also less commonly) phase
 transitions. Many different solutions have been suggested for overcoming these
-challenges. In this paper we will focus on Nested Sampling \citep{skilling}.
+challenges. This paper focuses on Nested Sampling \citep{skilling}.
 
@@
 The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
-should begin from the prior $\pi(\pars)$ and move through a sequence of
+should not solely be aimed at obtaining samples from the posterior distribution.
+By beginning from the prior $\pi(\pars)$ and moving through a sequence of
 distributions that successively compress the prior volume by a constant factor
-that is (approximately) known.
+that is (approximately) known, Nested Sampling can calculate posterior samples
+as well as the marginal likelihood or evidence
+$Z = \int p(\pars)p(\data = \data_{\rm actual} | \pars) \, d\pars$.
 

### 2014-03-06 ms.tex
Some words and refs

@@
 already imply a commitment to update from $p(\theta)$ to $p(\theta | \data)$
-once $\data$ becomes known.
+once $\data$ becomes known. For convenience, once the data set has been
+established and attention turns to computation, the prior is denoted by
+$\pi(\theta)$ and the likelihood function is $L(\theta)$.
 
@@
 \citep{simulated_tempering}, but uses NS's
-sequence of intermediate distributions instead of an annealed sequence.
-Retaining ``old'' distributions in the mixture allows
+sequence of intermediate distributions instead of an annealed sequence
+based on $\pi(\theta)L(\theta)^\beta$. Retaining ``old'' distributions in the
+mixture gives the particles a chance to explore more freely, perhaps escaping
+one mode in the distribution and moving to another.
+
+A multi-threaded, free software C++ implementation of Diffusive Nested Sampling
+is available online at {\tt http://github.com/eggplantbren/DNest3}.
 
 \section{Probabilistic Catalogs}
+Many questions in astronomy can be classified as ``source detection'' problems.
+Telescopes (whether optical, radio, or whatever) obtain some data, and we would
+like to use this data to infer the presence and properties of the objects in
+that part of the sky. Several different techniques and software packages have
+been developed for carrying this out \citep[e.g.][]{sextractor, dolphot}.
+However, this process
+can also be described as a Bayesian inference problem \citep{starfield}.
 The hypothesis space is the set of possible answers to the question
 ``how many objects are there, and what are their properties (positions, fluxes,
-etc)'' \citep{starfield}.
-
-%\section{Reverberation Mapping}
-%Many objects in the universe are too distant to resolve, so we cannot simply
-%``see'' what is going on. Rather we must infer what is going on. Active Galactic
-%Nuclei (AGN) are a good example.
+etc)''. The prior
 
@@
 \begin{thebibliography}{9}
+\bibitem[Bertin and
+Arnouts(1996)]{sextractor} Bertin, E., Arnouts, S.\ 1996.\ SExtractor: Software for source extraction.\ Astronomy and Astrophysics Supplement Series 117, 393-404.
 
@@
 1-13.
+
+\bibitem[Dolphin(2000)]{dolphot} Dolphin, A.~E.\ 2000, Publications of the
+Astronomical Society of the Pacific, 112, 1383
 

### 2014-03-07 ms.tex
Why dnest is godo

@@
 
-A multi-threaded, free software C++ implementation of Diffusive Nested Sampling
+A key advantage of DNS over standard MCMC-based Nested Sampling is the performance
+on multimodal distributions. With DNS, if two particles are in two separate
+but identical modes, there is no need for any deleting or copying of particles.
+The two particles will simply continue exploring their own modes. A particle is
+only deleted if it is unable to keep up with the bulk of the other particles.
+This way, the diversity created by having multiple starting points is maintained
+for as long as possible. A multi-threaded, free software C++ implementation of
+DNS, called {\tt DNest3},
 is available online at {\tt http://github.com/eggplantbren/DNest3}.
@@
 ``how many objects are there, and what are their properties (positions, fluxes,
-etc)''. The prior
+etc)''. This problem has been addressed from a Bayesian point of view by several
+authors \citep[e.g.][]{2003MNRAS.338..765H}.
 
@@
 
+\bibitem[Hobson 
+\& McLachlan(2003)]{2003MNRAS.338..765H} Hobson, M.~P., \& McLachlan, C.\ 2003, Monthly Notices of the Royal Astronomical Society, 338, 765
+
 \bibitem[Jaynes and Bretthorst(2003)]{jaynes} Jaynes, E.~T., 

### 2014-03-19 ms.tex
Acknowledgements
paragraph

@@
 
+Recently we investigated a Bayesian approach for finding objects in ``crowded
+fields'', small patches of the sky where many stars are visible in an image.
+Each star would appear as a point source in the image, except for the effects
+of blurring (caused by either diffraction as the light enters the telescope,
+or by atmospheric fluctuations), and the images are also typically noisy.
+
 \subsection{Models with known oversimplifications}
@@
 \begin{theacknowledgments}
-Acknowledgements.
+It is a pleasure to thank David W. Hogg (NYU), Daniel Foreman-Mackey (NYU),
+Fengji Hou (NYU), Anna Pancoast (UCSB), and
+John Skilling (MaxEnt Data Consultants) for valuable discussions.
 \end{theacknowledgments}

### 2014-03-20 ms.tex
Paragraph

@@
 or by atmospheric fluctuations), and the images are also typically noisy.
+Since the number of stars $N$ is itself unknown, we use reversible jump
+MCMC {\it within} DNS to infer $N$.
+
+For the ``easy'' simulated data set containing 100 stars, the information
+$H$ was approximately 500 nats, whereas for the ``hard'' dataset the information
+was $\sim$2600 nats. In both cases, the upward part of the DNS run was
+straightforward. However, in the ``hard'' case the diffusion phase of DNS
+is very slow. Unfortunately, I am presently unaware of any Nested Sampling
+method that only moves upwards in likelihood but is able to correct for the
+use of imperfect MCMC. Variations of annealing or tempering such as
+``annealed importance sampling'' and ``linked importance sampling'' \citep{ais, lis}
+have both these properties, suggesting this may be possible with NS as well.
 
@@
 It is a pleasure to thank David W. Hogg (NYU), Daniel Foreman-Mackey (NYU),
-Fengji Hou (NYU), Anna Pancoast (UCSB), and
+Fengji Hou (NYU), Anna Pancoast (UCSB), Benjamin Pope (Oxford), and
 John Skilling (MaxEnt Data Consultants) for valuable discussions.

### 2014-03-23 ms.tex
Added Neal references
massinf

@@
 Since the number of stars $N$ is itself unknown, we use reversible jump
-MCMC {\it within} DNS to infer $N$.
+MCMC {\it within} DNS to infer $N$. The model assumptions here are very similar
+to those suggested in \citep{massinf} for inferring positive additive
+distributions, but here the assumption that the underlying scene is composed
+of point sources is well justified, rather than a convenience.
 
@@
 
+\bibitem[Neal(1998)]{ais} Neal, R.~M.\ 1998.\ Annealed 
+Importance Sampling.\ ArXiv Physics e-prints arXiv:physics/9803008.
+
+\bibitem[Neal(2005)]{lis} Neal, R.~M.\ 2005.\ Estimating 
+Ratios of Normalizing Constants Using Linked Importance Sampling.\ ArXiv 
+Mathematics e-prints arXiv:math/0511216.
+
+\bibitem[Skilling(1998)]{massinf} Skilling, J.\ 1998.\ Massive 
+Inference and Maximum Entropy.\ Maximum Entropy and Bayesian Methods, 1.
+
 \bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, J., 2006, Nested Sampling for General Bayesian Computation, Bayesian Analysis 4, pp. 833-860.

### 2014-03-23 ms.tex
Figure (data)
Caption
Talk about the information

@@
 
+\begin{figure}
+%\begin{center}
+\includegraphics[scale=0.5]{Figures/data.pdf}
+\caption{The two simulated datasets originally studied 
+in \citet{starfield}. The ``easy'' image contains 100 stars and the
+``hard'' image contains 1000. The goal is to infer the number $N$ of stars
+in an image along with their positions and brightnesses.\label{fig:data}}
+%\end{center}
+\end{figure}
+
+One measure of the scale of an inference problem is the information
+$\mathcal{H}$, defined as the KL divergence from the prior to the posterior:
+\begin{eqnarray}
+\mathcal{H} = \int p(\pars | \data) \log\left[\frac{p(\pars | \data)}{p(\pars)}\right]\, d^n\pars
+\end{eqnarray}
+An intuitive interpretation of $\mathcal{H}$ is that it measures how small
+the posterior volume is relative to the prior. For example, if the prior
+were uniform over a volume $V$ and the posterior were uniform over a smaller
+volume $V'$, then $\mathcal{H}$ would equal $\log(V/V')$. Nested Sampling allows
+$\mathcal{H}$ to be calculated.
+
 For the ``easy'' simulated data set containing 100 stars, the information
-$H$ was approximately 500 nats, whereas for the ``hard'' dataset the information
+was approximately 500 nats, whereas for the ``hard'' dataset the information
 was $\sim$2600 nats. In both cases, the upward part of the DNS run was
 straightforward. However, in the ``hard'' case the diffusion phase of DNS
-is very slow. Unfortunately, I am presently unaware of any Nested Sampling
+is very slow. While the time taken to compress from the prior to the posterior
+in the upwards phase of DNS is proportional to $\mathcal{H}$, the time taken to
+diffuse from the prior to the posterior in the second phase of DNS is
+proportional to $\mathcal{H}^2$.
+Unfortunately, I am presently unaware of any Nested Sampling
 method that only moves upwards in likelihood but is able to correct for the

### 2014-03-23 ms.tex
notation fixes

@@
 this is not a ``derivation'' of Bayesian updating as the rules of probability
-already imply a commitment to update from $p(\theta)$ to $p(\theta | \data)$
+already imply a commitment to update from $p(\pars)$ to $p(\pars | \data)$
 once $\data$ becomes known. For convenience, once the data set has been
 established and attention turns to computation, the prior is denoted by
-$\pi(\theta)$ and the likelihood function is $L(\theta)$.
+$\pi(\pars)$ and the likelihood function is $L(\pars)$.
 
@@
 that is (approximately) known, Nested Sampling can calculate posterior samples
-as well as the marginal likelihood or evidence
-$Z = \int p(\pars)p(\data = \data_{\rm actual} | \pars) \, d\pars$.
+as well as the ``marginal likelihood'' or ``evidence''
+$\mathcal{Z} = \int \pi(\pars)L(\pars) \, d^n\pars$.
 
